--- 
title: "A Review of Concepts"
author: "Michael Eichenberger"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: mike4358/a-review-of-concepts
description: "This is a review of concepts."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

## Second-level header

Hi
```{r eval=TRUE}
library(reticulate)
x = 42
print(x)
```

```{python eval=FALSE}
# import pandas as pd
# 
# x = np.array([1,2,3])

#x = 42 * 2
print("hello")
```
$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$

### Third-level header 1

1. first
2. second
3. third

### Third-level header 2 {-}

sadf
`` `code` ``
