# Bookdown Examples {#examples}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(calc). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(linalg).

## Figures and tables example {#examples-figures-and-tables}

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

### Referencing {#examples-figures-and-tables-referencing}

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

## Citations {#examples-citations}

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

## Section example {#examples-section-1}

Here's some text in a section. Below are some examples of code chunks:

```{r test-chunk-r, eval=FALSE}
library(reticulate)

use_condaenv(condaenv = "r-reticulate")
scipy <- import("scipy")
scipy$amin(c(1,3,5,7))
pd <- import("pandas")
x <- pd$array(c(1,2,3))
print(x)
```

```{python test-chunk-python, eval=FALSE}
import numpy as np
import pandas as pd

x = np.array([1,2,3])
x = x * 2
print(x)
```

Now here's some math:

$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$

$\Gamma$

And now an equation:

\begin{equation}
  \frac{\Gamma\eta}{\iota}+\mu=15
  (\#eq:exampleequation)
\end{equation}

### Sub-section example 1 {#examples-section-3-subsection-1}

1. first
2. second
3. third

### Sub-section example 2 {#examples-section-3-subsection-2}

`` `code` ``


<!-- This calls a child rmd -->
```{r calc1child, child="example-subdirectory/example-1.Rmd", echo=FALSE}
```

<!-- 
```{block, type='FOO'}
Some text for this block.
```

```{r example-shiny-app, fig.cap='Example Shiny App.'}
  knitr::include_app(' https://mike4358.shinyapps.io/temp-shiny/', height = '600px')
```
-->
